---
title: "Day1_InteractiveSession2"
author: "Scout Leonard"
date: "8/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

### Logs and exponents in R

Some examples of using the `log()` function and the `exp()` **function** in R.

*Command + Option + "I" is the keyboard shortcut for inserting a code chunk.*

```{r}
# Examples of logarithms 

log(4)

#Example of exponents

exp(5)

log(exp(1))
```


### Creating Sequences of Values 

```{r}
# A sequence from 1 to 20, by increments of 1 

ex_1 <- seq(from= 1, to =20, by = 20)

#Vector from 0 to 40 by increments of 0.2

ex_2 <- seq(from= 0, to = 40, by = 0.2)

#vector from 0 to 5000 by increments of 10

ex_3 <- seq(from =0, to= 5000, by = 10)
```

### Create a Function for Logistic Growth 

Given the carrying capacity, the initial population, the growth rate,and a time, use the logistic growth model to estimate the population at that time. 

```{r}
pop_logistic <- function(capacity, init_pop, rate, time_yr) {
  
  capacity / ( 1 + ((capacity - init_pop)/ init_pop) * exp(-rate*time_yr))
  
  
}

pop_logistic(capacity = 2580, init_pop = 230, rate = 0.32, time_yr = 2.4)
```


### Try finding the population over a sequence of times 

```{r}

#Create a vector of times from 0 to 20 by increments of 0.5

time_vec <- seq(from =0, to = 15, by = 0.5)

```

# Now let's estimate the population over that range of times, given capacity = 2580, initial population = 230, rate = 0.32. 

```{r}
chipmunk_pop <- pop_logistic(capacity = 3000, init_pop = 230, rate = 0.32, time_yr = time_vec)
```

### Create a dataframe and plot chipmunk population over time 

```{r}

chipmunk_df <- data.frame(time_vec, chipmunk_pop)

chipmunk_df
```


#### Create a bare minimum ggplot graph: 

```{r}
ggplot(data = chipmunk_df, aes(x = time_vec, y = chipmunk_pop)) + 
  geom_point() + 
  labs(x = "Time (years)",
       y = "Chipmunk population (individuals)",
       title = "Inyo NF chipmunks",
       subtitle = "yay chipmunks")
```

