---
title: "Practice Problems Section 3 & 4"
author: "Scout Leonard"
date: "8/3/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

library(palmerpenguins)
```

# Section 3: Derivatives in R
## First Order univariate derivations
### Find the derivative expression and slope at the indicted value for the following functions

```{r}
fx <- expression(x^2)

df_dx <- D(expr = fx, name = 'x')

x <- 3

eval(expr = df_dx)

```

```{r}
pa <- expression(2*(3*a + 2)^4)

dp_da <- D(expr = pa, name = 'a')
a <- 1.2
eval(expr = dp_da)
```

```{r}
gt <- expression(((-4*t)/(t^2 + 1)^3))

dg_dt <- D(expr = gt, name = 't')

t <- 0

eval(expr = dg_dt)
```

## Higher order univariate derivatives: 

#### Find the second derivative with respect to z
```{r}
gz <- expression(4.6 - 1.9*z^3)

dg_dz <- D(expr = gz, name = 'z')
d2g_d2z <- D(expr = dg_dz, name = 'z')
d2g_d2z
```

## Partial derivatives 
#### Find all partials of the function 

```{r}
fxyz <- expression((2*(x^2)*y) - 3*x + 1 + (4*(z^4)*x))

df_dx <- D(expr = fxyz, name = 'x')
df_dx


df_dy <- D(expr = fxyz, name = 'y')
df_dy

df_dz <- D(expr = fxyz, name = 'z')
df_dz
```

# Section 4: Make Some Plots 

#### Make a plot of the function for x values from -0.5 to +0.5

```{r}
eq <- function(x){
  (2.4*exp(-0.05*x))*sin(x)
  
}

ggplot(data = data.frame(x = c(-0.5, 0.5)), aes( x = x)) +
  stat_function(fun = eq)
```

#### Create a ggplot of penguin bill length versus bill depth using the penguins dataset with point color on dependent species

```{r}
ggplot(data = penguins, aes(x = bill_length_mm, y = bill_depth_mm)) +
  geom_point(aes(color = species))
```


#### Make a jitterplot of flipper length by species (species on x axis, flipper length on y axis). Update axis labels and add title. 
```{r}
ggplot(data = penguins, aes(x = species, y = flipper_length_mm)) +
  geom_jitter() +
  labs(x = "Species",
       y = "Flipper Length (mm)",
       title = "Palmer Penguins Flipper Length by Species",
       caption = "Data collected by KB Gorman et al. at Palmer")
```


#### Jitter plot specaes out the x values in a way that is more visually appealing 
```{r}
ggplot(data = penguins, aes(x = species, y = flipper_length_mm)) +
  geom_point() +
  labs(x = "Species",
       y = "Flipper Length (mm)",
       title = "Palmer Penguins Flipper Length by Species",
       caption = "Data collected by KB Gorman et al. at Palmer")
```

