---
title: "Logicals"
author: "Scout Leonard"
date: "8/6/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

## Taking a look at `starwars`

- `include = ` to show of hide everything
- `echo = ` to show or hide code 

```{r, include=FALSE}
# Summary of starwars

summary(starwars)

#Look at the first few lines
head(starwars)

#Look at the last few lines
tail(starwars)

#check out dimensions
dim(starwars)
```

#Scatterplot with character height on x axis, character weight on y axis 


- `eval=` stops evaluation when you knit
- `warning=` hides warnings from the knit product 
```{r, eval=FALSE}
ggplot(data = starwars, aes(x = height, y = mass)) +
  geom_point(color = "purple")
```

## Find the mean, variance, and standard deviation of character height 

```{r}
sw_height_mean <- mean(starwars$height, na.rm = TRUE)
sw_height_mean

# Default of mean function is not to exclude NA data, as a clue that you have missing values! `na.rm` removes NA data  

# Using similar naming, find: 
# Variance of character height (var())

sw_variance <- var(starwars$height, na.rm = TRUE)
sw_variance
# (unit is cm^2)

# Standard deviation of character height (sd())
sw_sd <- sd(starwars$height, na.rm = TRUE)
sw_sd
# (unit is cm)
```

## In line R code: enhance reproducibility! 

Mean character height is `r round(sw_height_mean, 1)` cm, with a standard deviation of `r round(sw_sd, 1)` cm. 

## Logical Expressions

They ask questions lile 'does this match?' or 'is this less than __?'

```{r}
5 < 10

#Also works for alphabetical order 
"cat" > "armadillo"

"cat" > "elephant"

"dog" == "dog"


```



```{r}
10 <= 11

5>= 4

3<=1
```

```{r}
tarantulas <- c(1,3,7,10,15)

tarantulas > 5 
```

## Logical operators: 

- Negation: `!`
- And: `&`
- Or: `|`

```{r}
3 < 1 | 8 > 2

6 < 10 & 5 < 1 

7 != 11

4 != 4 | 2 < 5 | 6 >10

0 == TRUE

0 == FALSE

1 == TRUE

1 == FALSE

# R stores 0s as false and 1s as true 
```

